Leadership across cultures and contexts: an exploratory analysis

### 2020-05-18 leadership_across_cultures_contexts.Rmd
Added some ggsaves to SI.

```{r subsisttree, fig.cap="The area of the entire rectangle represents the total number of text records in the study data (N = 2012). The nested rectangles represent (from smallest to largest) the proportion of text records in each document, culture, and subsistence strategy."}

plot_cult_docs_subsis
```

@@

```{r doc-years, fig.height=6, fig.cap="Historgram of eHRAF document publiction year. Vertical line shows the median publication year."}
doc_year_hist
```

@@

```{r field-years, fig.height=8, fig.width=9, fig.cap="Span of fieldwork years of study documents. To improve clarity, one document with very early fieldwork from 1791-1804 was omitted."}
doc_fielddates_plot
```

@@

ggplot(all_data) + 
  geom_mosaic(aes(x = product(subsistence, region), fill = subsistence)) +
  scale_fill_viridis(discrete = T) + 
  scale_x_productlist(labels = lbls) +
  guides(fill = guide_legend(reverse = T)) +
  labs(x = '', y = '') +
  theme_minimal(15)
```

@@

```{r eHRAFpages, fig.height=8, fig.cap="Scatterplot of the number of leadership text records versus the total number of pages of ethnography in the eHRAF. Each dot is one culture. Line fit by loess regression."}
plot_pages_tr
```

@@

```{r pubdate, fig.cap=glue_data(list(n=length(all_study_vars)), "The effect of publication date on the probability of finding evidence for leader qualities, functions, benefits, and costs. Multivariate values are  controlling for female authorship and number of pages of ethonography for each culture. All models had random intercepts for ethnographers nested within cultures. Models were fit for each of the {n} dimensions as outcomes, and after adjusing p-values for a false discovery rate of 5%, the effect of publication date on these outcome dimensions remained significant. Publication date was centered and standardized by 1 SD. Each dot is one coefficient (converted from log odds to odds ratios). Bars are 95% CI.")}
plot_pubdate
```

@@

@@

```{r heatmapgroups, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each group context. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

p_heatmap_groups + theme_minimal(15)
```

```{r heatmapsubsis, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each subsistence strategy. Estimated marginal means were standardized by rows, and therefore can only be compared within rows, i.e., the colors represent the relative amount of evidence across levels of the categorical predictor within the same outcome variable."}

p_heatmap_subsis + theme_minimal(15)
```

```{r heatmapregion, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each continental region. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

p_heatmap_region + theme_minimal(15)
```

```{r heatmapsex, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by leader sex. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}

p_heatmap_sex + theme_minimal(15)
```

@@

```{r FunctionRE, fig.cap="Ethnographer and Culture random effects for function variables."}
plot_fun_auth_cult_re
```

```{r QualityRE, fig.cap="Ethnographer and Culture random effects for quality variables."}
plot_qual_auth_cult_re
```

@@

@@

@@

```{r logisticpcafunc, fig.height=8, fig.width=10, fig.cap="Logistic PCA of leader function variables with two principal components."}
logisticPCA_loadings_plot(m_lpca_func, df_func)
```

```{r lpcafuncbiplot, fig.cap="Function variable PC scores for each text record. Colors represent text records that had evidence for a function variable that loaded highly on either PC1 or PC2 (but no evidence for the other high-loading variables). Mixed: evidence for two or more of high-loading variables."}
plot_lpca_func
```

```{r logisticpcaqual, fig.height=10, fig.width=10, fig.cap="Logistic PCA of leader quality variables with two principal components."}
logisticPCA_loadings_plot(m_lpca_qual, df_qual)
```

```{r lpcaqualbiplot, fig.cap="Quality variable PC scores for each text record. Colors represent text records that had evidence for a quality variable that loaded highly on either PC1 or PC2 (but no evidence for the other high-loading variables). Mixed: evidence for two or more of high-loading variables."}
plot_lpca_qual
```

@@

We also explored the degree to which our feature variables varied by our four factors by comparing similar mixed effects models with either only intercepts or with the four factors. See Table \@ref(tab:featurecoefs) for AIC values and coefficients. The *Cultural conformity* feature model was not improved by the inclusion of the four factors as predictors, however the models predicting the other `r (length(features)-1)` feature variables were improved with the predictive factors (see Figure \@ref(fig:heatmapdrop1)B in the main text. We again used drop1 AIC comparison to identify which factors improved the models. Only leader sex and group structure improved model fit. See Figure \@ref(fig:heatmap_feature_sex) and Figure \@ref(fig:heatmapfeaturegroups). These results largely correspond to interpretations of our leadership dimension models previously discussed.

```{r featurecor, fig.cap="Feature variable correlation matrix. Values are correlation coefficients."}
plot_feature_cor
```

@@

```{r heatmapfeaturesex, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each feature variable by leader sex. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}
heatmap_feature_sex
```

```{r heatmapfeaturegroups, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each feature variable by group context. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}
heatmap_feature_groups
```

>>>>

```{r subsisttree, fig.cap="The area of the entire rectangle represents the total number of text records in the study data (N = 2012). The nested rectangles represent (from smallest to largest) the proportion of text records in each document, culture, and subsistence strategy."}
ggsave(filename = 'Figures/plot_cult_docs_subsis.pdf', plot_cult_docs_subsis)
plot_cult_docs_subsis
```

@@

```{r doc-years, fig.height=6, fig.cap="Historgram of eHRAF document publiction year. Vertical line shows the median publication year."}
ggsave(filename = 'Figures/doc_year_hist.pdf', doc_year_hist)
doc_year_hist
```

@@

```{r field-years, fig.height=8, fig.width=9, fig.cap="Span of fieldwork years of study documents. To improve clarity, one document with very early fieldwork from 1791-1804 was omitted."}
ggsave(filename = 'Figures/doc_fielddates_plot.pdf', doc_fielddates_plot)
doc_fielddates_plot
```

@@

reg_sub_plot<-ggplot(all_data) + 
  geom_mosaic(aes(x = product(subsistence, region), fill = subsistence)) +
  scale_fill_viridis(discrete = T) + 
  scale_x_productlist(labels = lbls) +
  guides(fill = guide_legend(reverse = T)) +
  labs(x = '', y = '') +
  theme_minimal(15)
ggsave(filename = 'Figures/reg_sub_plot.pdf', reg_sub_plot)
reg_sub_plot
```

@@

```{r eHRAFpages, fig.height=8, fig.cap="Scatterplot of the number of leadership text records versus the total number of pages of ethnography in the eHRAF. Each dot is one culture. Line fit by loess regression."}
ggsave(filename = 'Figures/plot_pages_tr.pdf', plot_pages_tr)
plot_pages_tr
```

@@

```{r pubdate, fig.cap=glue_data(list(n=length(all_study_vars)), "The effect of publication date on the probability of finding evidence for leader qualities, functions, benefits, and costs. Multivariate values are  controlling for female authorship and number of pages of ethonography for each culture. All models had random intercepts for ethnographers nested within cultures. Models were fit for each of the {n} dimensions as outcomes, and after adjusing p-values for a false discovery rate of 5%, the effect of publication date on these outcome dimensions remained significant. Publication date was centered and standardized by 1 SD. Each dot is one coefficient (converted from log odds to odds ratios). Bars are 95% CI.")}
ggsave(filename = 'Figures/plot_pubdate.pdf', plot_pubdate)
plot_pubdate
```

@@

ggsave(filename = 'Figures/status_theplots.pdf', ((theplots[[1]] / theplots[[2]]) | (theplots[[3]] / theplots[[4]])) + plot_annotation(title = 'Predictors of leader status', tag_levels = 'A'))

@@

```{r heatmapgroups, fig.width=11, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each group context. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}
ggsave(filename = 'Figures/heatmap_groups.pdf', p_heatmap_groups + theme_minimal(15))
p_heatmap_groups + theme_minimal(15)
```

```{r heatmapsubsis, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each subsistence strategy. Estimated marginal means were standardized by rows, and therefore can only be compared within rows, i.e., the colors represent the relative amount of evidence across levels of the categorical predictor within the same outcome variable."}
ggsave(filename = 'Figures/heatmap_subsis.pdf', p_heatmap_subsis + theme_minimal(15))
p_heatmap_subsis + theme_minimal(15)
```

```{r heatmapregion, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by each continental region. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}
ggsave(filename = 'Figures/heatmap_region.pdf', p_heatmap_region + theme_minimal(15))
p_heatmap_region + theme_minimal(15)
```

```{r heatmapsex, fig.width=10, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each outcome variable by leader sex. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}
ggsave(filename = 'Figures/heatmap_sex.pdf', p_heatmap_sex + theme_minimal(15))
p_heatmap_sex + theme_minimal(15)
```

@@

```{r FunctionRE, fig.cap="Ethnographer and Culture random effects for function variables.", fig.width=11}
ggsave(filename = 'Figures/plot_fun_auth_cult_re.pdf', plot_fun_auth_cult_re)
plot_fun_auth_cult_re
```

```{r QualityRE, fig.cap="Ethnographer and Culture random effects for quality variables.", fig.width=11}
ggsave(filename = 'Figures/plot_qual_auth_cult_re.pdf', plot_qual_auth_cult_re)
plot_qual_auth_cult_re
```

@@

ggsave(filename = 'Figures/totalbenfits_theplots.pdf', ((theplots[[1]] / theplots[[2]]) | (theplots[[3]] / theplots[[4]])) + plot_annotation(title = 'Predictors of leader benefits', tag_levels = 'A'))

@@

ggsave(filename = 'Figures/totalcosts_theplots.pdf', theplots[[1]] / theplots[[2]] + plot_annotation(title = 'Predictors of leader costs', tag_levels = 'A'))

@@

```{r logisticpcafunc, fig.height=8, fig.width=10, fig.cap="Logistic PCA of leader function variables with two principal components."}
ggsave(filename = 'Figures/logpca_func_loadinds.pdf', logisticPCA_loadings_plot(m_lpca_func, df_func))
logisticPCA_loadings_plot(m_lpca_func, df_func)
```

```{r lpcafuncbiplot, fig.cap="Function variable PC scores for each text record. Colors represent text records that had evidence for a function variable that loaded highly on either PC1 or PC2 (but no evidence for the other high-loading variables). Mixed: evidence for two or more of high-loading variables."}
ggsave(filename = 'Figures/logpca_funcbiplot_loadinds.pdf', plot_lpca_func)
plot_lpca_func
```

```{r logisticpcaqual, fig.height=10, fig.width=10, fig.cap="Logistic PCA of leader quality variables with two principal components."}
ggsave(filename = 'Figures/logpca_qual_loadinds.pdf', logisticPCA_loadings_plot(m_lpca_qual, df_qual))
logisticPCA_loadings_plot(m_lpca_qual, df_qual)
```

```{r lpcaqualbiplot, fig.cap="Quality variable PC scores for each text record. Colors represent text records that had evidence for a quality variable that loaded highly on either PC1 or PC2 (but no evidence for the other high-loading variables). Mixed: evidence for two or more of high-loading variables."}
ggsave(filename = 'Figures/logpca_qualbiplot_loadinds.pdf', plot_lpca_qual)
plot_lpca_qual
```

@@

We also explored the degree to which our feature variables varied by our four factors by comparing similar mixed effects models with either only intercepts or with the four factors. See Table \@ref(tab:featurecoefs) for AIC values and coefficients. The *Cultural conformity* feature model was not improved by the inclusion of the four factors as predictors, however the models predicting the other `r (length(features)-1)` feature variables were improved with the predictive factors (see Figure \@ref(fig:heatmapdrop1)B in the main text. We again used drop1 AIC comparison to identify which factors improved the models. Only leader sex and group structure improved model fit. See Figure \@ref(fig:heatmapfeaturesex) and Figure \@ref(fig:heatmapfeaturegroups). These results largely correspond to interpretations of our leadership dimension models previously discussed.

```{r featurecor, fig.cap="Feature variable correlation matrix. Values are correlation coefficients."}
ggsave(filename = 'Figures/plot_feature_cor.pdf', plot_feature_cor)
plot_feature_cor
```

@@

```{r heatmapfeaturesex, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each feature variable by leader sex. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}
ggsave(filename = 'Figures/heatmap_feature_sex.pdf', heatmap_feature_sex)
heatmap_feature_sex
```

```{r heatmapfeaturegroups, fig.cap="Heatmap of relative estimated marginal means of the levels of evidence for each feature variable by group context. Estimated marginal means were standardized by rows. The colors therefore represent the relative amount of evidence within the same outcome variable."}
ggsave(filename = 'Figures/heatmap_feature_groups.pdf', heatmap_feature_groups)
heatmap_feature_groups
```
